On the number of tiles visited by a\\ line segment on a rectangular grid

### 2022-01-19 paper.tex
Errata / wording

An equivalent formulation of the problem is obtained allowing segments of length $\len$ \emph{or smaller}. The equivalence is clear from the fact that reducing the length cannot increase the number of visited tiles. Either of these formulations will be referred to as the \emph{direct} problem.

The \emph{inverse} problem \ref{prob: determ inv} is, given $\tiles \in \mathbb N$, to determine the infimum length of all segments that visit at least $\tiles$ tiles. If the length can take any real value the infimum is not a minimum, because given any segment can be shortened by some small amount without changing the number of visited tiles. This is a consequence of the interior of each tile being an open set.

>>>>

An equivalent formulation of the problem is obtained by allowing segments of length $\len$ \emph{or smaller}. The equivalence is clear from the fact that reducing the length cannot increase the number of visited tiles. Either of these formulations will be referred to as the \emph{direct} problem.

The \emph{inverse} problem \ref{prob: determ inv} is, given $\tiles \in \mathbb N$, to determine the infimum length of all segments that visit at least $\tiles$ tiles. If the length can take any real value the infimum is not a minimum, because given any segment it can be shortened by some small amount without changing the number of visited tiles. This is a consequence of the interior of each tile being an open set.
